---
title: "Extra Credit Seung Min Song"
output:  
  pdf_document: default
html_document:
  includes:
  in_header: header.html
css: ./lab.css
highlight: pygments
theme: cerulean
toc: true
toc_float: true
linkcolor: blue
date: "2022-09-13"
---
Team member: Ted Kim\
GitHub: <https://github.com/seung-m1nsong/607>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r install-packages, echo=FALSE}

arrPackages <- c('RMySQL', 'DBI', 'dplyr', 'tidyverse', 'ggplot2')
installed_packages <- arrPackages %in% rownames(installed.packages())

if (any(installed_packages == FALSE)) {
  install.packages(arrPackages[!installed_packages], 
                   repos = "http://cran.us.r-project.org")
}
invisible(lapply(arrPackages, library, character.only = TRUE))
```

Create a connection object to MySQL database.
```{r dbconnect-data, echo=TRUE}
con <- DBI::dbConnect(
  RMySQL::MySQL(), 
  user="root", 
  password="",
  host="localhost", 
  dbname="stock"
)
```

Create database *stock* if not exists, and use database *stock*
```{r create-database, echo=TRUE}
res <- dbSendQuery(con, 'create database if not exists stock;')
res <- dbSendQuery(con, 'use stock;')
```

Insert data to sp table
```{r get-data, results='asis', echo=TRUE}
dfsp <- read.csv('https://raw.githubusercontent.com/seung-m1nsong/607/main/Extracredit/stockprice.csv')
dbWriteTable(con, 'sp', dfsp, row.names=FALSE, overwrite=TRUE)
```

Change data type using R
```{r dboverwrite-data}
dbWriteTable(con, 'sp', dfsp, field.types=c(tradingdate='date', closeprice='double(8,2)', volume='bigint', open='double(8,2)', high='double(8,2)', low='double(8,2)', symbol='varchar(10)'),  row.names=FALSE, overwrite=TRUE)
```

## Year to date Average

sql
```{r}
dfyeartodateavg <- DBI::dbGetQuery(con, 
"select
	symbol, tradingdate, 
    closeprice, avg(closeprice) over (partition by symbol order by tradingdate asc) as avg_closeprice,
    volume, avg(volume) over (partition by symbol order by tradingdate asc) as avg_volume,
    high, avg(high) over (partition by symbol order by tradingdate asc) as avg_high,
    low, avg(low) over (partition by symbol order by tradingdate asc) as avg_low
from
	sp
where
	symbol = 'amd';")
dfyeartodateavg
```

R for amd
```{r order-by-preceding-amdytd, echo=TRUE}
ytd <- dfsp[order(dfsp$tradingdate), 
             c('symbol', 'tradingdate', 'closeprice', 'high')] %>%
        filter(symbol == 'amd') %>%
        mutate (
          ytd_closeprice = cummean(closeprice),
          ytd_high = cummean(high)
        )
print(ytd[, c('symbol','tradingdate','closeprice','ytd_closeprice','high','ytd_high')])
```
R for intc
```{r order-by-preceding-intcytd, echo=TRUE}
ytd <- dfsp[order(dfsp$tradingdate), 
             c('symbol', 'tradingdate', 'closeprice', 'high')] %>%
        filter(symbol == 'intc') %>%
        mutate (
          ytd_closeprice = cummean(closeprice),
          ytd_high = cummean(high)
        )
print(ytd[, c('symbol','tradingdate','closeprice','ytd_closeprice','high','ytd_high')])
```


## Six day Moving Average

Sql
```{r}
dfamdsixdaymoving <- DBI::dbGetQuery(con, 
"select
	symbol, tradingdate,
    closeprice, avg(closeprice) over (order by tradingdate rows between 5 preceding and current row) as `smd_avg_price`,
	volume, avg(volume) over (order by tradingdate rows between 5 preceding and current row) as sdm_avg_volume,
	high, avg(high) over (order by tradingdate rows between 5 preceding and current row) as sdm_avg_high,
	low, avg(low) over (order by tradingdate rows between 5 preceding and current row) as sdm_avg_low
from
	sp
where
	symbol = 'amd' and tradingdate <= '2022-01-10'
order by
	symbol, tradingdate asc;")
dfamdsixdaymoving 
```

R for amd
```{r order-by-preceding-amdsixday, echo=TRUE}
moving_avg <- function(x, n) {
  res <- c()
  for(i in 1:length(x)){
    res <- c(res, ifelse(i < n, mean(x[1:i]), mean(x[(i-(n-1)):i])))
  }
  return(res)
}

dfsixdaymoving <- dfsp %>%
  filter(tradingdate < "2022-01-10" & symbol == 'amd') %>%
  mutate (
   moving_avg = moving_avg(closeprice, 6)
  )

print(dfsixdaymoving)
```

R for intc
```{r order-by-preceding-intcsixday, echo=TRUE}
moving_avg <- function(x, n) {
  res <- c()
  for(i in 1:length(x)){
    res <- c(res, ifelse(i < n, mean(x[1:i]), mean(x[(i-(n-1)):i])))
  }
  return(res)
}

dfsixdaymoving <- dfsp %>%
  filter(tradingdate < "2022-01-10" & symbol == 'intc') %>%
  mutate (
   moving_avg = moving_avg(closeprice, 6)
  )

print(dfsixdaymoving)
```


The argument transmitted as a function in mutate is an object or a variable.\

For example, if the column name is closeprice, the entire closeprice column is transmitted as one object [ex. c('10', '20', '30', '40',…) or 1, 'a', etc.] \

In addition, the return value from the function must have the same number of elements as the elements originally transmitted.\

The moving_avg() function requires two arguments. The first argument accepts a column as a vector. The second factor is the number of rows to be treated as variables. The logic is very simple. First, generates an object **res <- c()** for return. Then, executes for…loop statement for number of element.  In the case of the 'six-day moving average', if the variable *i* is less than or equal to 5, only an average from 1 to the current *i* value is obtained. And if the variable *i* exceeds 5, an average of the current *i* value and the previous five values are obtained.\

x = vector (column with values of data frame)
n = number variable (2-day, 3-day, 4-day, ..., n-day)
i = index of x -> 1 to length(x)
res = result variable to return
res <- c(res, value) -> res = (1), res <- c(res, 2) then res = (1, 2)

moving_avg <- function(x, n) {
  res <- c()
  for(i in 1:length(x)){
    res <- c(res, ifelse(i < n, mean(x[1:i]), mean(x[(i-(n-1)):i])))
  }
  return(res)
}

[example]
x = (1, 2, 3, 4, 5, 6, 7, 8, 9, 10)
n = 6
i = 1 -> res = (1)
i = 2 -> res = (1, 1.5)
i = 3 -> res = (1, 1.5, 2)
i = 4 -> res = (1, 1.5, 2, 2.5)
i = 5 -> res = (1, 1.5, 2, 2.5, 3)
i = 6 -> res = (1, 1.5, 2, 2.5, 3, 3.5)
i = 7 -> res = (1, 1.5, 2, 2.5, 3, 3.5, 4.5)
i = 8 -> res = (1, 1.5, 2, 2.5, 3, 3.5, 4.5, 5.5)
i = 9 -> res = (1, 1.5, 2, 2.5, 3, 3.5, 4.5, 5.5, 6.5)
i = 10 -> res = (1, 1.5, 2, 2.5, 3, 3.5, 4.5, 5.5, 6.5, 7.5)